Learning GENERAL Principles from\\Hundreds of Software Projects

### 2020-02-12 response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               RESPONSE TO REVIEWERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
\newpage
\renewcommand*{\thesection}{\Alph{section}}
\nobalance
\section*{RESPONSE TO REVIEWERS}
\section*{Comments from the editor}

\review{I would like to thank the authors for submitting their work to TSE. While all the reviewers agree that the problem addressed is important and the paper has potential, the reviewers also identified several concerns that need to be carefully addressed. The reviewers also agreed that the amount of work needed to address those concerns is beyond a major revision. Thus, after carefully checking the reviewers and in accordance with reviewer’s recommendations, I also recommend “Revise and resubmit as New”.}

Thank you very much for your encouraging comments. We have made appropriate changes to the manuscript taking into careful consideration the recommendations of the reviewers. We hope that this new draft adequately satisfies all the issues raised by the reviewers. To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.

Below is the brief summary of our changes:
\be
\item The problem statement needs to be clarified and properly positioned (R1, R3). XXX

\item The novelty of the approach needs to be clarified (R3). XXX (see \bareresp{2-1})

\item The writing needs to be improved (R1, R2, R3).

\item The study needs to include all the details to ensure replicability (R1, R2).

\item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).

\item The background on transfer learning needs citations (R2).
\ee

\section*{Reviewer 1}

Thank you very much for your detailed review. We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.

\review{(1.1) 1. Background. The paper builds upon a number of previous studies. However, several key questions have no answer: *What is* the bellwhether? *Why is* this relevant? How does it work when applied to different contexts? Why is this useful in practice? None of these questions are addressed in the paper. This submission should be self-contained and allow a reader to understand its content without reading 10 other papers; in this sense, the submission fails completely. For example, the paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}

### 2020-02-12 manuscript.tex
Updates from Overleaf

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color}
\usepackage[labelfont=bf,textfont={bf}]{caption}
\usepackage{subcaption}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{boxedminipage}
\usepackage{notoccite}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{minted}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{lipsum}
\usetikzlibrary{shadows}
\usepackage{mathtools}
 \usepackage{paralist}
 \definecolor{light-gray}{gray}{0.80}
\usepackage{graphics}
\usepackage[shortlabels]{enumitem}
%\usepackage{balance}
\usepackage{dblfloatfix}

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
  emphstyle=\bfseries\color{black!80} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true%
                ]{{\small  ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\begin{document}
\title{  Learning GENERAL Principles \\from Hundreds of     Projects}

@@

\IEEEtitleabstractindextext{%
\begin{abstract}

This paper seeks scalable methods for learning general lessons from hundreds of software projects.
When one   exemplar project (the ``bellwether'') offers the best advice, it can be used to offer    advice for
many others. These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).  Such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
for software quality issues).

But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
Hence,  we  propose GENERAL:  a novel bellwether based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For example, the defect prediction models found by GENERAL from
nearly 700 projects were  just as good as those found via  traditional methods.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction, Scalable Method. 
\end{IEEEkeywords}}

@@

In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
  tremendous practical significance.  When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),
 Further, since the bellwether is equivalent to the other models,
 then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (just by applying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

@@

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects is better than learning just from your own project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods.
For example:
\bi
\item
This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

\item 
 Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
 is inherently more scalable.
 \ei
\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figs/cost.png}
    \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
    \label{fig:cost}
\end{figure} 
Using GENERAL, we can  explore five research questions:

\begin{itemize}
        \item 
            \textbf{RQ1}:  What are the drawbacks of traditional bellwether  methods?

            \begin{RQ}{
                With hundreds of projects, traditional bellwether methods can discover  source datasets which offer general lessons for all the rest. But this traditional approach can require hundreds of hours of computations and will not scale to larger data sets.  }
            \end{RQ}

        \item 
            \textbf{RQ2}: How to tame complexity of bellwether?

             \begin{RQ}{
                The proposed new  transfer learner called GENERAL uses hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
            \end{RQ}

        \item 
            \textbf{RQ3}:  Is this faster bellwether effective?

            \begin{RQ}{
                The new transfer learner GENERAL  is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
            \end{RQ}

        \item 
            \textbf{RQ4}: Does learning from too many projects have detrimental effect?

            \begin{RQ}{
                Based on the results seen in this study we can see learning from too many projects does have a detrimental effect in-term of predictive power and shows conclusion instability.}
            \end{RQ}

        \item 
            \textbf{RQ5}: What exactly did we learn from all those projects?

            \begin{RQ}{
                Based on the results seen in this study, our best models uses only a fraction of the features in the dataset. Looking at the selected metrics, we can conclude that in these 697 projects, code interface issues are the dominant factor on software defects. }
            \end{RQ}

    \end{itemize}
Overall, the  contributions of this paper are
\bi

\item \textbf{Hierarchical bellwethers for  transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm GENERAL to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner. The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{GENERAL}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.

\item \textbf{Showing inherent generality in SE}  In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).

@@

The rest of this paper is structured as follows. . Some background and related work are discussed in section~\ref{sec:literature}. Our algorithm GENERAL is described in section~\ref{GENERAL}. Data collection and experimental setup are in section~\ref{sec:Data Collection}. Followed by evaluation criteria in section~\ref{eval} and performance measures in section~\ref{sec:Measures}. The results and answers to the research questions are presented in section~\ref{sec:results}, which is followed by threats to validity in section~\ref{sec:validity}. Finally the conclusion is provided in section~\ref{sec:concl}.

@@

\begin{figure}[!b]
    \centering
    \includegraphics[width=\linewidth]{figs/predictive_power.png}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:predictive_power}
\end{figure}

@@

The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering. Consider the hypothetical results of Figure~\ref{fig:predictive_power}. The \textcolor{ao(english)}{{\bf GREEN}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e. higher levels in the hierarchical cluster). After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1. In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level. Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.

@@

In this section, we ask ``Why even bother to transfer lessons learned between projects?''. In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e. general models outperformed by specialized models localized to particular parts of the data. Menzies et al. showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective than rules learned from the global dataset. While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models. While local can cause conclusion instabilities, global models can miss details which are specific to a certain dataset. So in this study, we review the evidence that if it is useful to explore more than just the local data. This evidence falls into four groups:

@@

\ei
Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list? Where would you get the data, from enough projects, to   successfully refute the above? And where would you get that data? And how would you draw conclusions from that large set?

@@

\bi
\item
\textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
\item    
 \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
\ei
Another way to divide transfer learning is the approach that is followed. There are  2 approaches that are frequently used in many research: {\bf similarity-based approaches} and {\bf dimensional transforms}.

 \textbf{Similarity-Based Approaches:} In this approach we can transfer some/all subset of the rows or columns of data from source to target. For example, the Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $. However, the Burak filter suffered from the all too common instability problem (here, whenever the source or target is updated, data miners will learn a new model since different code modules will satisfy the k = 10 nearest neighbor criteria). Other researchers ~\cite{kocaguneli2012, kocaguneli2011find} doubted that a fixed value of k was appropriate for all data. That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``varianc'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves). This method combined row selection with row pruning (of nearby rows with large variance). Other similarity methods~\cite{Zhang16aa} combine domain knowledge with automatic processing: e.g. data is partitioned using engineering judgment before automatic tools cluster the data. To address variations of software metrics between different projects, the original metric values were discretized by rank transformation according to similar degree of context factors.

@@

% \begin{figure}[!t]
%     \small
%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
%     ~~~~~~\inputminted[numbersep=1pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/bubble.py}
%     %\vspace{-0.2cm}
%     \caption{Pseudo-code of GENERAL Experiment}
%     \label{fig:GAP_pseudocode} 
%     %\vspace{-0.3cm}
% \end{figure}

% \begin{figure}[!t]
%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
%         \begin{minipage}{\linewidth}
%             \inputminted[numbersep=2pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/heirarchical_bellw.py}
%         \end{minipage}
%     %\vspace{-0.2cm}
%     \caption{Pseudo-code of Hierarchical Bellwether}
%     \label{fig:GAP_pseudocode} 
%     %\vspace{-0.3cm}
% \end{figure}

@@

Prior to anything else, we must summarize our projects.  Xenos \cite{Xenos} distinguishes
between {\em product metrics} (e.g.  counts of lines
of code );  and  {\em process metrics} 
about the  development process (e.g.    number of file revisions).
Using the   Understand tool~\cite{visualize},
we   calculated 21 product and 5 process metrics to build     defect prediction models
 (see Table~\ref{tbl:metric}).
 These product  metrics are
 calculated from snapshots from every 6 months of the data. The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color}
\usepackage[labelfont=bf,textfont={bf}]{caption}
\usepackage{subcaption}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{boxedminipage}
\usepackage{notoccite}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{enumerate}
\usepackage{booktabs}
% \usepackage{minted}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{lipsum}
\usetikzlibrary{shadows}
\usepackage{mathtools}
 \usepackage{paralist}
 \definecolor{light-gray}{gray}{0.80}
\usepackage{graphics}
\usepackage[shortlabels]{enumitem}
%\usepackage{balance}
\usepackage{dblfloatfix}

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}

\newcommand{\tbl}[1]{Table~\ref{tbl:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.7}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{darkgray}{rgb}{0.47, 0.47, 0.47}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
  emphstyle=\bfseries\color{black!80} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true%
                ]{{\small  ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\begin{document}
\title{  Learning GENERAL Principles from\\Hundreds of    Software Projects}

@@

\IEEEtitleabstractindextext{%
\begin{abstract}
When one   exemplar project, which we call the ``bellwether'', offers the best advice
then
it can be used to offer    advice for
many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects. 
% Such general conclusions   simplifies     software quality policies since the list of quality problems, and their mitigations, is static). Also such general conclusions simplify the design and delivery
% of training programs since, as long as the bellwether offers best advice,
% then  ``best practices'' will remain  now constant.
% Lastly, bellwethers simplify tool development
% since, using the advice from the bellwether,  it is clear where it is most cost-effective to buy/build tools to mitigate
% for software quality issues.

But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For example, for nearly 700 projects,
the defect prediction models generated from GENERAL's bellwether  
were  just as good as those found via  standard methods.

% Having shown that it is
% possible to transfer lessons learned across
%  100s of projects, our future work
%  will be to  achieve ``mega-transfer'';
%  i.e. to transfer lessons learned between
%  1000s to 10,000s of projects.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction, Software Analytics. 
\end{IEEEkeywords}}

@@

In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
  tremendous practical significance.  When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by studying the bellwether),
 Further, since the bellwether is equivalent to the other models,
 then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

@@

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects can be better than learning just from your own local project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods.
For example:
\bi
\item
This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

\item 
 Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
 is inherently more scalable.
 \ei
\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figs/cost.pdf}
    \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
    \label{fig:cost}
\end{figure} 
Using GENERAL, we can  explore these research questions:

            \textbf{RQ1}:   Can hierarchical clustering tame the complexity of bellwether-based reasoning?

            \begin{RQ}{
               Theoretically and empirically, the 
hierarchical
reasoning on GENERAL performs much
faster than standard bellwether methods.}
            \end{RQ}

           \noindent \textbf{RQ2}:  Is this faster bellwether effective?

            \begin{RQ}{
                Measured in terms of predictive performance,
the effectiveness of hierarchical bellwethers
is very similar to local learning
(and these two methods are more effective
than the other options explored here).}
            \end{RQ}

       \noindent 
            \textbf{RQ3}: Does learning from too many projects have detrimental effect?

            \begin{RQ}{
            Assessed in terms of {\em recall},
it is better to learn bellwethers from more data rather than less.
But assessed in terms of {\em false alarms}, 
while learning bellwethers
from many projects is useful, it is possible to learn from too much data.}
            \end{RQ}

         \noindent 
            \textbf{RQ4}: What exactly did we learn from all those projects?

            \begin{RQ}{
                The importance of many key features is not apparent at the local
level. To fully appreciate the critical impact on defects
of class interface design,  it is necessary to conduct
a global analysis across hundreds of projects. }
            \end{RQ}

\noindent Overall, the  contributions of this paper are
\bi

\item \textbf{Hierarchical bellwethers for  transfer learner:} We
offer a  novel hierarchical clustering    bellwether algorithm  called GENERAL  (described in section~\ref{GENERAL}) that
finds bellwether in hierarchical clusters, then promotes those bellwether to upper levels
The final  project that is promoted to the root of the hierarchy is returned as  ``the'' bellwether.

\item \textbf{Showing inherent generality in SE:}
In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).

@@

\ei
The rest of this paper is structured as follows. Some background and related work are discussed in section~\ref{sec:literature}. Our algorithm GENERAL is described in section~\ref{GENERAL}. Data collection and experimental setup are in section~\ref{sec:Data Collection}. Followed by evaluation criteria in section~\ref{eval} and performance measures in section~\ref{sec:Measures}. The results and answers to the research questions are presented in section~\ref{sec:results}, which is followed by threats to validity in section~\ref{sec:validity}. Finally the conclusion is provided in section~\ref{sec:concl}.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figs/predictive_power.pdf}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:predictive_power}
\end{figure}

@@

The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering. Consider the hypothetical results of Figure~\ref{fig:predictive_power}. The \textcolor{blue}{{\bf BLUE}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e. higher levels in the hierarchical cluster). After about learning from 1000 projects, the \textcolor{blue}{{\bf BLUE}} curve's growth stops and we would say that community size here was around cluster size in level 1. In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level. 
%Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.

@@

In this section, we ask ``Why even bother to transfer lessons learned between projects?''. In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e. general models outperformed by specialized models localized to particular parts of the data.
For example.
Menzies et al. explored local vs global learning in defect prediction and effort estimation~\cite{menzies2012local}  and found that
 learning rules from specific local data was more
 effective than learning rules from the global space.

On the other hand,
Herbold et al.~\cite{herbold2017global}  offered an opposite conclusion.
In their   study regarding global vs local model for cross-project defect prediction,
they saw that  local models offered little to no improvement over models learned
from all the global data.
One explanation for this discrepancy  is the size of number of projects that they explored.
Menzies, Herbold et al. explored less than two dozen projects which raises issues of external validity in their conclusions. Accordingly, here,  we explore nearly 700 projects. As shown below, the results of this paper agree  more with Herbold et al. than  Menzies et al. since we show that one global model (learned from a single bellwether projects) does just as well as anything else.

Apart from the above discrepancy in research results, there are many other reasons to
explore learning from many projects. Those reasons   falls into four groups:

@@

\ei
Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list? Where would you get the data, from enough projects, to   successfully refute the above? And where would you get that data? And how would you draw conclusions from that large set? Note that the answers to these questions requires learning from multiple projects. Hence, this paper.

@@

\bi
\item    
 \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.

\item
\textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
This paper explores scalable methods for  homogeneous transfer.
\ei
Another way to divide transfer learning is the approach that is followed. There are  2 approaches that are frequently used in many research: {\bf similarity-based approaches} and {\bf dimensional transforms}.

 \textbf{Similarity-Based Approaches:} In this approach we can transfer some/all subset of the rows or columns of data from source to target. For example, the Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $. However, the Burak filter suffered from the all too common instability problem (here, whenever the source or target is updated, data miners will learn a new model since different code modules will satisfy the k = 10 nearest neighbor criteria). Other researchers ~\cite{kocaguneli2012, kocaguneli2011find} doubted that a fixed value of k was appropriate for all data. That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``variance'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves). This method combined row selection with row pruning (of nearby rows with large variance). Other similarity methods~\cite{Zhang16aa} combine domain knowledge with automatic processing: e.g. data is partitioned using engineering judgment before automatic tools cluster the data. To address variations of software metrics between different projects, the original metric values were discretized by rank transformation according to similar degree of context factors.

@@

@@

Prior to anything else, we must summarize our projects.  Xenos \cite{Xenos} distinguishes
between {\em product metrics} (e.g.  counts of lines
of code );  and  {\em process metrics} 
about the  development process (e.g.    number of file revisions).
Using the   Understand tool~\cite{visualize},
we   calculated 21 product and 5 process metrics to build     defect prediction models
 (see Table~\ref{tbl:metric}).
 These product  metrics are
 calculated from snapshots from every 6 months of the data. The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.   The data collected for this project is summarized in \fig{lang_projects}
 and \fig{meta}.

\begin{figure}[!b]
\centering
{\small \renewcommand{\baselinestretch}{0.7}
\begin{tabular}{rrl}
    \textbf{Language} & \textbf{Projects} & \\
    Java & 290 &\crule{41.6pt}{8pt} \\
    CPP & 241 &\crule{34.5pt}{8pt} \\
    C & 116 &\crule{16.6pt}{8pt} \\
    CS & 42 &\crule{6.3pt}{8pt} \\
    Pascal & 8 &\crule{1.1pt}{8pt} \\
     & 
\end{tabular}}
\caption{Distribution of projects depending on languages.
Many  projects use combinations of languages to
achieve their results. Here, we show majority language used in each project.}
\label{fig:lang_projects}
\end{figure}
